How has the Brazilian Amazon been constructed as a problem:Presidential speeches and transnational politics since 1985

### 2022-09-22 Draft_September_2022/Full_draft_20220901.rmd
Updated table for model in appendix

\newpage

@@

modelsummary::modelsummary(list("Conservation" = model_logit_con2,
                                "Economic Integration" = model_logit_ei2,
                                "Social Development" = model_logit_sd2,
                                "Sovereignty" = model_logit_sov2),
                           title = "Odds Ratio and Confidence Intervals",
                           exponentiate = TRUE, statistic = "conf.int")

>>>>

@@

modelsummary::modelsummary(list("Conservation" = model_logit_con2,
                                "Economic Integration" = model_logit_ei2,
                                "Social Development" = model_logit_sd2,
                                "Sovereignty" = model_logit_sov2),
                           exponentiate = TRUE, statistic = "conf.int",
                           coef_rename = c("thousand_km" = "1000 km",
                                        "def_year" = "Yearly Deforestation",
                                        "AAI" = "Average Yearly Inflation",
                                        "election_year" = "Election Year",
                                        "(Intercept)" = "Constant"),
                           stars = TRUE,
                           title = "Odds Ratio and Confidence Intervals")
```
